%%%%%%%%%%%%
% Basic setup

\documentclass[11pt]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage{fullpage}
\usepackage{etaremune}
\usepackage{setspace}
\usepackage{geometry} 
\usepackage{textcomp}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{enumitem}

\newcommand\myshade{85}
\colorlet{linkcolor}{Maroon}

\setstretch{1}

%%%%%%%%%%%%
% PDF setup
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi
\hypersetup{
    letterpaper,
    colorlinks,
    linkcolor=linkcolor!\myshade!black,
    urlcolor=linkcolor!\myshade!black,
    pdfpagemode=none,
    pdftitle={Siddharth Mishra-Sharma's CV},
    pdfauthor={Siddharth Mishra-Sharma},
    pdfsubject={Siddharth Mishra-Sharma's CV},
    pdfkeywords={}
}
%%%%%%%%%%%%

%%%%%%%%%%%%
% Margin setup
\oddsidemargin=-0.4in
\evensidemargin=-0.4in
\textwidth=7.2in
\headheight=-0.6in
\topmargin=0.0in
\textheight=10.in
%\footheight 1.0in 
%%%%%%%%%%%%

%%Custom commands
%
%% In case you need to adjust margins:
%%\topmargin=-0.5in      
%\evensidemargin=-0.5in     
%\oddsidemargin=-0.5in      
%\textwidth=7.2in        
%%\textheight=9.9in       
%\headsep=0.25in         
%
%
%% Setup the header and footer
%\pagestyle{fancy}                                                      
%\cfoot{Page\ \thepage\ of\ 2}                                                               
%%\rfoot{}                         
%\renewcommand\headrulewidth{0.0pt}                                     
%\renewcommand\footrulewidth{0.4pt}  

\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\hyphenchar\font=-1

% Change bullet size
\makeatletter
\renewcommand\@biblabel[1]{\textbullet}
\makeatother

% Packed itemize environment
\newenvironment{packed_itemize}{
\begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}]
  \setlength{\itemsep}{3pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}

% Packed enumerate environment
\newenvironment{packed_enumerate}[1][]{
\begin{etaremune}[#1]
  \setlength{\itemsep}{3pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{etaremune}
}

%-----------------------------------------------------------
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.8in}{l@{\extracolsep{\fill}}r}
		{#1} & {#2} \\
		{#3} & {#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

% \usepackage{fancyhdr}

% \fancypagestyle{style1}{
% \fancyhf{}
% \fancyhead[C]{style 1 with thin line}
% \fancyfoot[C]{\thepage}
% \renewcommand{\headrulewidth}{0.4pt}
% }

% \fancypagestyle{style2}{
% \fancyhf{}
% \fancyhead[C]{STYLE 2 WITH THICK LINE}
% \fancyfoot[C]{= \thepage{} =}
% \renewcommand{\headrulewidth}{1pt}
% }

\begin{document}

%% Heading
\begin{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
&\huge{\textbf{\sc{Siddharth Mishra-Sharma}}}&   \\
& 726 Broadway, New York, NY 10003, USA &\\

% &\
&\faEnvelopeO\hspace{1mm}\href{mailto:sm8383@nyu.edu}{\texttt{sm8383@nyu.edu}} 
~\faGlobe\hspace{1mm}\href{https://smsharma.github.io}{\texttt{smsharma.github.io}} 
~\faMobile\hspace{1mm}\href{tel:16099330103}{+1 609-933-0103} 
% ~\faGithub\hspace{1mm}\href{https://github.com/smsharma}{\texttt{github.com/smsharma}} &
\vspace{0.5mm}
\\ 

\hline\hline

\end{tabular*}
\end{center}

\vspace{2.0mm}

%% Appointments 
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Academic Appointments}}\\
\hline
\end{tabular*}

% NYU
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{New York University}  & \textbf {New York, NY, USA}\\
{Center for Cosmology and Particle Physics} \vspace{1mm}\\
{Postdoctoral Associate}  & {Sep. 2018 -- Present} \vspace{.0mm} \\  
\end{tabular*}
    
\vspace{4.0mm}

%% Education 
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Education}}\\
\hline
\end{tabular*}

% Princeton
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Princeton University}  & \textbf {Princeton, NJ, USA}\vspace{1mm}\\
{Ph.D. in Physics}  & {Sep. 2013 -- Aug. 2018} \vspace{.0mm} \\  
\small{Advisor: Mariangela Lisanti}& {} \vspace{.0mm} \\
\small{Thesis: \href{https://dataspace.princeton.edu/jspui/handle/88435/dsp012v23vx15d}{\emph{Extragalactic Searches for Dark Matter Annihilation}}}& {} \vspace{2mm} \\
% \small{M.A. awarded in Jan. 2015}& {} \vspace{2mm} \\

\end{tabular*}

% Cambridge
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{University of Cambridge}  & \textbf {Cambridge, UK}\vspace{1mm}\\
{Part III of the Mathematical Tripos (M.Math.)} & {Oct. 2012 -- Jun. 2013}\vspace{0.2mm}\\ 
% \small{\emph{Specializing in Theoretical Physics}}\vspace{1mm}\\
{B.A. (Hons.) in Natural Sciences (Physical)} & {Oct. 2009 -- Jun. 2012} \\
% \small{\emph{Specializing in Physics}}\vspace{1mm}\\
\end{tabular*}
%\small{M.A. (Cantab) awarded in May 2016. \small{\emph{Note that this is an academic rank that may be given six years after the end of a first term at the University of Cambridge, and is not a postgraduate qualification.}}}\vspace{0mm}\\

\vspace{4.0mm}

%% Publications 

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Publications}}\\
\hline
\vspace{.3mm}
\end{tabular*}
% \vspace{1.5mm}

\noindent
Primary contributions \emph{(except where indicated with an asterisk\,$^*$, authors are listed in alphabetical order as per the standard in particle physics)}:

\begin{packed_enumerate}[start=24]

\item $^*$S. Mishra-Sharma and K. Cranmer, \emph{Semi-parametric $\gamma$-ray modeling with Gaussian processes and variational inference}, submitted to the Machine Learning and the Physical Sciences Workshop at NeurIPS 2020,  \href{https://arxiv.org/abs/2010.10450}{[arXiv:2010.10450]}

\item A. Caputo, H. Liu, S. Mishra-Sharma, M. Pospelov, J.T. Ruderman, A. Urbano, \emph{Edges and Endpoints in 21-cm Observations from Resonant Photon Production}, under review in Phys.Rev.Lett. \href{https://arxiv.org/abs/2009.03899}{[arXiv:2009.03899]}

\item $^*$J.J. Somalwar, L.J. Chang, S. Mishra-Sharma, M. Lisanti, \emph{Harnessing the Population Statistics of Subhalos to Search for Annihilating Dark Matter}, under review in Astrophys.J. \href{https://arxiv.org/abs/2009.00021}{[arXiv:2009.00021]}

\item A. Caputo, H. Liu, S. Mishra-Sharma, J.T. Ruderman, \emph{Modeling Dark Photon Oscillations in Our Inhomogeneous Universe}, under review in Phys.Rev. \textbf{D}  \href{https://arxiv.org/abs/2004.06733}{[arXiv:2004.06733]}

\item S. Mishra-Sharma, K. Van Tilburg, N. Weiner, \emph{Power of Halometry}, \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.102.023026}{Phys.Rev. \textbf{D102} (2020) 023026} [Editors' Suggestion and Featured in \emph{Physics}; \href{https://physics.aps.org/articles/v13/s98}{Synopsis}]  \href{https://arxiv.org/abs/2003.02264}{[arXiv:2003.02264]}

\item $^*$M. Buschmann, N.L. Rodd, B.R. Safdi, L.J. Chang, S. Mishra-Sharma, M. Lisanti, O. Macias \emph{Foreground Mismodeling and the Point Source Explanation of the Fermi Galactic Center Excess},  \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.102.023023}{Phys.Rev. \textbf{D102} (2020) 023023} \href{https://arxiv.org/abs/2002.12373}{[arXiv:2002.12373]} 

\item A. Caputo, H. Liu, S. Mishra-Sharma, J.T. Ruderman, \emph{Dark Photon Oscillations in Our Inhomogeneous Universe}, accepted to Phys.Rev.Lett. \href{https://arxiv.org/abs/2002.05165}{[arXiv:2002.05165]}

\item $^*$J. Brehmer, K. Cranmer, S. Mishra-Sharma, F. Kling, G. Louppe,  \emph{Mining gold: Improving simulation-based inference with latent information} \href{https://ml4physicalsciences.github.io/files/NeurIPS_ML4PS_2019_16.pdf}{[Paper]}, \href{https://ml4physicalsciences.github.io/}{Machine Learning and the Physical Sciences Workshop at the 33rd Conference on Neural Information Processing Systems (NeurIPS)}

\item $^{*\dagger}$J. Brehmer, $^\dagger$S. Mishra-Sharma, J. Hermans, G. Louppe, K. Cranmer, \emph{Mining for Dark Matter Substructure: Inferring subhalo population properties from strong lenses with machine learning}, \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab4c41}{Astrophys.J. \textbf{886} (2019) no.1, 49} \href{https://arxiv.org/abs/1909.02005}{[arXiv:1909.02005]} ($^\dagger$\emph{Equal contribution})

\item $^*$L.J. Chang, S. Mishra-Sharma, M. Lisanti, M. Buschmann, N.L. Rodd, B.R. Safdi, \emph{Characterizing the Nature of the Unresolved Point Sources in the Galactic Center: An Assessment of Systematic Uncertainties},  \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.101.023014}{Phys.Rev. \textbf{D101} (2020) 023014} \href{https://arxiv.org/abs/1908.10874}{[arXiv:1908.10874]}, 

\item L.J. Chang, M. Lisanti, S. Mishra-Sharma, \emph{Search for Dark Matter Annihilation in the Milky Way Halo}, \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.123004}{Phys.Rev. \textbf{D98} (2018) 123004} \href{https://arxiv.org/abs/1804.04132}{[arXiv:1804.04132]}

\item $^*$S. Mishra-Sharma, D. Alonso, J. Dunkley, \emph{Neutrino masses and beyond-$\Lambda$CDM cosmology with LSST and future CMB experiments}, \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.123544}{Phys.Rev. \textbf{D97} (2018) 123544}  \href{https://arxiv.org/abs/1803.07561}{[arXiv:1803.07561]}

\item R. Bartels, D. Hooper, T. Linden, S. Mishra-Sharma, N.L. Rodd, B.R. Safdi, T.R. Slatyer, \emph{Comment on ``Characterizing the population of pulsars in the Galactic bulge with the
{\it Fermi} Large Area Telescope'' [arXiv:1705.00009\MakeLowercase{v}1]}, \href{https://www.sciencedirect.com/science/article/pii/S2212686418300268}{Phys.Dark Univ. \textbf{20} (2018) 88-94} \href{https://arxiv.org/abs/1710.10266}{[arXiv:1710.10266]}

\item M. Lisanti, S. Mishra-Sharma, N.L. Rodd, B.R. Safdi, \emph{Mapping Extragalactic Dark Matter Annihilation with Galaxy Surveys: A Systematic Study of Stacked Group Searches},  \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.97.063005}{Phys.Rev. \textbf{D97} (2018) 063005} \href{https://arxiv.org/abs/1709.00416}{[arXiv:1709.00416]}

\item M. Lisanti, S. Mishra-Sharma, N.L. Rodd, B.R. Safdi, \emph{Search for Dark Matter Annihilation in Galaxy Groups},  \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.120.101101}{Phys.Rev.Lett. \textbf{120} (2018) 101101} \href{https://arxiv.org/abs/1708.09385}{[arXiv:1708.09385]}

\item T. Cohen, M. Lisanti, H. K. Lou, S. Mishra-Sharma, \emph{LHC Searches for Dark Sector Showers},  \href{https://link.springer.com/article/10.1007/JHEP11(2017)196}{JHEP \textbf{11}, 196 (2017)}  \href{https://arxiv.org/abs/1707.05326}{ [arXiv:1707.05326]}

\item S. Mishra-Sharma, N.L. Rodd, B.R. Safdi, \emph{NPTFit: A code package for Non-Poissonian Template Fitting},  \href{http://iopscience.iop.org/article/10.3847/1538-3881/aa6d5f/meta}{Astron.J. \textbf{153} (2017) no.6, 253}  \href{https://arxiv.org/abs/1612.03173}{ [arXiv:1612.03173]}

\item Y. Kahn, G. Krnjaic, S. Mishra-Sharma, T.M.P. Tait, \emph{Light Weakly Coupled Axial Forces: Models, Constraints, and Projections},  \href{https://link.springer.com/article/10.1007%2FJHEP05%282017%29002}{JHEP \textbf{05}, 002 (2017)}  \href{https://arxiv.org/abs/1609.09072}{[arXiv:1609.09072]}

\item M. Lisanti, S. Mishra-Sharma, L. Necib, B.R. Safdi, \emph{Deciphering Contributions to the Extragalactic Gamma-Ray Background from 2 GeV to 2 TeV},  \href{http://iopscience.iop.org/article/10.3847/0004-637X/832/2/117/meta}{Astrophys.J. \textbf{832} (2016) no.2, 117} \href{https://arxiv.org/abs/1606.04101}{[arXiv:1606.04101]}

\item S.K. Lee, M. Lisanti, S. Mishra-Sharma, B.R. Safdi, \emph{Modulation Effects in Dark Matter-Electron Scattering Experiments}, \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.92.083517}{Phys.Rev. \textbf{D92} (2015) 083517} \href{https://arxiv.org/abs/1508.07361}{[arXiv:1508.07361]}

\end{packed_enumerate}

\noindent
Contributions to white papers and as part of large collaborations:

\begin{packed_enumerate}[start=4]

\item J. Alimena \emph{et al.}, \emph{Searching for long-lived particles beyond the Standard Model at the Large Hadron Collider}  \href{https://iopscience.iop.org/article/10.1088/1361-6471/ab4574}{J.Phys.G 47 (2020) 090501} \href{https://arxiv.org/abs/1903.04497}{[arXiv:1903.04497]}, 

\item S. Algeri \emph{et al.}, \emph{Statistical challenges in the search for dark matter} \href{https://arxiv.org/abs/1807.09273}{[arXiv:1807.09273]}

\item DarkSide Collaboration, \emph{Constraints on Sub-GeV Dark Matter-Electron Scattering from the DarkSide-50 Experiment}, \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.121.111303}{Phys.Rev.Lett. \textbf{121} (2018) 111303} \href{https://arxiv.org/abs/1802.06998}{[arXiv:1802.06998]}

\item DarkSide Collaboration, \emph{Low-Mass Dark Matter Search with the DarkSide-50 Experiment}, \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.121.081307}{Phys.Rev.Lett. \textbf{121} (2018) 081307}  \href{https://arxiv.org/abs/1802.06994}{[arXiv:1802.06994]}


\end{packed_enumerate}

%% Prizes and Honours 

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Prizes and Honours}}\\
\hline
\end{tabular*}\vspace{1.5mm}
\begin{packed_itemize}
\item Department Teaching Award, Princeton Department of Physics  \hfill 2018 \\ \emph{Awarded for excellence in the role of Assistant in Introduction for courses taught at Princeton.}
\item Kusaka Memorial Prize in Physics, Princeton Department of Physics \hfill 2017 \\ \emph{Awarded to physics graduate students who have shown outstanding performance in research and professional promise.}
\item Princeton Graduate School Impact Award \hfill 2016 \\ \emph{Awarded to an individual in the community that has made a difference during their time at Princeton.}
\item Princeton First-Year Graduate Fellowship \hfill 2013 \\ \emph{Awarded for the first year of graduate study at Princeton.}
\item Hugo de Balsham Prize  \hfill 2012 \\ \emph{Awarded for exceptional academic distinction at Peterhouse, Cambridge.}
\item Peter Scheuer Scholarship in Natural Sciences \hfill 2011, 2012 \\ \emph{Awarded for exceptional academic performance in Cambridge second/third year Tripos examinations.}
\item Senior Academic Scholarship of Peterhouse, Cambridge \hfill 2010\\ \emph{Awarded for exceptional academic performance in Cambridge first year Tripos examinations.}
\end{packed_itemize}

\newpage

%% Talks 

\vspace{2.0mm}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Seminars and Conference Talks}}\\
\hline
\end{tabular*}\vspace{3.5mm}

\noindent
Invited talks:
\begin{packed_itemize}
\item BSM PANDEMIC Seminar \href{https://www.bsmpandemic.com/ }{\texttt{bsmpandemic.com}} (Remote talk) \hfill Nov. 2020
\item SLAC Elementary Particle Physics Seminar (Remote talk) \hfill Jul. 2020
\item University of Amsterdam GRAPPA Colloquium (Remote talk) \hfill May 2020
\item Princeton Pheno \& Vino Seminar (Remote talk) \hfill Apr. 2020
\item CERN-TH BSM Forum (Remote talk) \hfill  Apr. 2020
\item Machine Learning for Astrophysicists Seminar \href{https://docs.google.com/document/d/1GGtE-YIuAWlmpKSr38_kyiF-Fklszhkh4FkiYWzBAho/pub}{\texttt{mlclub.net}} (Remote talk) \hfill  Mar. 2020
\item Michigan LCTP Brown Bag Seminar \hfill Ann Arbor, MI, Jan. 2020
\item Stony Brook University Particle Physics Seminar \hfill Stony Brook, NY, Nov. 2019
\item Minnesota High Energy Theory Lunchtime Seminar \hfill  Minneapolis, MN, Nov. 2019
\item Brown Astrophysics Seminar Series \hfill Providence, RI, May 2019
\item NYU CCPP Brown Bag Seminar \hfill New York, NY, Apr. 2019
\item Particles, Strings and Cosmology (PASCOS) 2018 \hfill Cleveland, OH, Jun. 2018
\item Recontres de Blois 2018 \hfill Blois, France, Jun. 2018
\item Princeton Astrophysics/IAS Cosmology Lunch Seminar \hfill Princeton, NJ, May 2018
\item Fermilab Particle Astrophysics Seminar \hfill Batavia, IL, Mar. 2018
\item Workshop on Statistical Challenges in the Search for Dark Matter \hfill Banff, Canada, Feb. 2018
\item Maryland Elementary Particle Theory Seminar \hfill College Park, MD, Nov. 2017
\item Rutgers High Energy Theory Seminar \hfill New Brunswick, NJ, Nov. 2017
\item Cornell Particle Theory Seminar \hfill Ithaca, NY, Nov. 2017
\item Caltech Particle Theory Seminar \hfill Pasadena, CA, Oct. 2017
\item UC Irvine Joint Particle Seminar \hfill Irvine, CA, Oct. 2017
\item ICTP LHC Long-Lived Particles Community Workshop (Remote talk) \hfill Oct. 2017
\item Oxford Dalitz Seminar in Fundamental Physics  \hfill Oxford, UK, Oct. 2017
\item KIPAC Tea Talk  \hfill Stanford, CA, Sep. 2017
\item UC Santa Cruz Institute for Particle Physics Seminar  \hfill Santa Cruz, CA, Sep. 2017
\item Berkeley 4D Seminar  \hfill Berkeley, CA, Sep. 2017
\item Princeton Pheno \& Vino Seminar \hfill Princeton, NJ, Apr. 2017
\item MIT BSM Journal Club \hfill Boston, MA, Nov. 2016
\end{packed_itemize}

\noindent
Contributed talks:
\begin{packed_itemize}
  \item WFIRST Science Meeting (Flatiron Institute) \hfill New York, NY, Mar. 2020
  \item LSST Dark Matter Workshop \hfill Chicago, IL, Aug. 2019
  \item SUSY 2019 \hfill Corpus Christi, TX, May 2019
  \item Phenomenology Symposium (Pheno) 2019 \hfill Pittsburgh, PA, May 2019
  \item Dark Matter, Neutrinos and their Connection (DA$\nu$CO) \hfill Odense, Denmark, Aug. 2017
  \item TeV Particle Astrophysics (TeVPA) 2017 \hfill Columbus, OH, Aug. 2017 
  \item Phenomenology Symposium (Pheno) 2017 \hfill Pittsburgh, PA, May 2017 
  \item APS April Meeting 2017 \hfill Washington, DC, Jan. 2017 
  \item TeV Particle Astrophysics (TeVPA) 2016 \hfill Geneva, Switzerland, Sep. 2016 
  \item Gamma Rays and Dark Matter Workshop \hfill Obergurgl, Austria, Dec. 2015
  \item Phenomenology Symposium (Pheno) 2015 \hfill Pittsburgh, PA, May 2015
  
\end{packed_itemize}

% \newpage

%% Summer schools and workshops

\vspace{2.0mm}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Workshops and Schools}}\\
\hline
\end{tabular*}\vspace{1.5mm}
\begin{packed_itemize}
\item \emph{Gaia} Sprint 2019 \hfill Santa Barbara, CA, Mar. 2019
\item Accelerating the Search for Dark Matter with Machine Learning \hfill Leiden, Netherlands, Jan. 2018
\item Prospects in Theoretical Physics (PiTP) \hfill Princeton, NJ, Jul. 2017
\item Theoretical Advanced Study Institute (TASI) \hfill Boulder, CO, Jun. 2016
\item Tri-Institute Summer School on Elementary Particles (TRISEP) \hfill Waterloo, Canada, Jul. 2015
\end{packed_itemize}

%% Teaching 

\vspace{2.0mm}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Teaching Experience}}\\
\hline
\vspace{.0mm}
\end{tabular*}
\vspace{0.2mm}
\emph{Course numbers refer to courses taught at Princeton.}
\begin{packed_itemize}
\item PHY235 Introduction to Research in Physics \hfill Spring 2018
\item PHY312 Experimental Physics \hfill Spring 2018
\item PHY115  Physics for Future Leaders \hfill Fall 2017
\item PHY104  General Physics II \hfill Spring 2016
\item PHY406 Nuclear and Elementary Particle Physics \hfill Fall 2015
\item PHY106 Advanced Physics (Electromagnetism) \hfill Spring 2015
\item MAT201 Calculus III (Multivariable Calculus) \hfill Fall 2014, 2015
\item PHY105 Advanced Physics (Mechanics) \hfill Fall 2014
\end{packed_itemize}

\vspace{2.0mm}

%% Broader impact
 
\vspace{2.0mm}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Broader Impact and Community}}\\
\hline
\end{tabular*}\vspace{1.5mm}
\begin{packed_itemize}
\item \emph{Reviewer}, Phys.Rev. {D}, Phys.Rev.Lett., Comput.Phys.Commun., JHEP,\hfill 2017 -- Present \\ NeurIPS Machine Learning and the Physical Sciences Workshop
\item \emph{Organizer}, NYU CCPP Particle Physics Seminar \hfill 2019 -- 2020
% \item \emph{Member}, Princeton University Student Life Committee \hfill 2016 -- 2018
% \item \emph{Member}, Princeton Graduate Housing Advisory Board \hfill 2016 -- 2018
\item \emph{Vice Chair}, Princeton Graduate College House Committee \hfill 2016 -- 2018
\item \emph{Subject Representative}, Princeton Graduate Student Government Assembly \hfill 2013 -- 2017
\item \emph{Organizer}, Princeton Physics Department Open House Committee  \hfill 2015 -- 2016
\item \emph{Chair}, Princeton Physics Graduate Student Council \hfill 2015 -- 2018
\end{packed_itemize}
\vspace{2.0mm}

% \vspace{2.0mm}


%% Work Experience

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{Research Training}}\\
\hline
\end{tabular*}

\begin{packed_itemize}
\item CERN \hfill Geneva, Switzerland \\ \emph{Visiting Student, CMS Experiment} \hfill Aug. -- Sep. 2012
\item DAMTP, University of Cambridge \hfill Cambridge, UK \\ \emph{Summer Student} \hfill Jun. -- Jul. 2012
\item Institute of Astronomy, University of Cambridge \hfill Cambridge, UK \\ \emph{Summer Student} \hfill Aug. -- Sep. 2011
\item CERN \hfill Geneva, Switzerland \\ \emph{Summer Student, CMS Experiment} \hfill Jun. -- Jul. 2011

\end{packed_itemize}

%% Work Experience

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc \Large{References}}\\
\hline
\end{tabular*}

\begin{packed_itemize}
  \item Mariangela Lisanti (Princeton University) \hfill \href{mailto:mlisanti@princeton.edu}{\texttt{mlisanti@princeton.edu}}
  \item Neal Weiner (New York University) \hfill \href{mailto:neal.weiner@nyu.edu}{\texttt{neal.weiner@nyu.edu}}
  \item Kyle Cranmer (New York University) \hfill \href{mailto:kyle.cranmer@nyu.edu}{\texttt{kyle.cranmer@nyu.edu}}
  \item Joshua Ruderman (New York University) \hfill \href{mailto:ruderman@nyu.edu}{\texttt{ruderman@nyu.edu}}
  \item Christoph Weniger (University of Amsterdam) \hfill \href{mailto:c.weniger@uva.nl}{\texttt{c.weniger@uva.nl}}

\end{packed_itemize}


\vspace*{\fill}

\end{document}
